%% -------------------------------------------------
%%      Work Experience
%% -------------------------------------------------



% \divider

% \cvevent{Higher Secondary Certificate}{Cantonment Public School and College}{2008}{Rangpur,Bangladesh}
% {GPA : 5.00/5.00}

% \divider

% \cvevent{Secondary School Certificate}{Cantonment Public School and College}{2006}{Rangpur,Bangladesh}
% {GPA : 5.00/5.00}

% \divider

\cvsection{Research Projects}
\vspace{-5pt}

    \cvproject{CPU and GPU Accelerated Fully Homomorphic Encryption (FHE) [2019]}
    \begin{itemize}
        \item The objective is to improve the performance of FHE schemes by designing efficient parallel frameworks. I first formulate the algebraic operations on generic $n$-bit numbers. The projects uses include parallelization both in CPU and GPU. Experimentally, the project achieves a speedup of $20\times$ for any 32-bit boolean operation and $14.5\times$ for multiplications (approx.).
        \item The ongoing projects are to device extensive mathematical model for exhaustive computations such as: Logistic Regression, and Deep learning. In short, the machine learning framework over encrypted data will be used for computing any model over sensitive data.
    \end{itemize}
    
    \cvproject{Parallel Linear Regression over Encrypted Data [2018]}
    \begin{itemize}
        \item This project proposes an approximate mathematical model utilizing linear regression on homomorphically encrypted data to predict the disease association of an individual. Furthermore, as these encryption schemes are not efficient considering computation time, we incorporate the multi-core parallelism to make the framework realistic. (Speed up $7\times$ approx.).
    \end{itemize}


\cvsection{Professional Projects}
\vspace{-5pt}
\cvproject{Digital Evidence Management System [2017]}
\begin{itemize}
    \item A device wide (desktop, android, and iOS) application to collect and store the evidences of digital crimes. The applications has web scrappers inside and an admin panel (Spring boot). The server-client communication model is REST API.
\end{itemize}

\cvproject{A2 Milk Bar [2016]}
\begin{itemize}
    \item The food ordering services for \textit{A2 Milk Bar} (Australia) for iPhone users based customers’ location (swift v2.1). The project had PHP Laravel framework and MySql as database for admin panel.
\end{itemize}

\cvproject{Content Management System (CMS) [2014]}
\begin{itemize}
    \item This application was built to provide the desired contents to the client.
    % websites with minimal effort. 
    The framework was built using Django framework and MySql as database.
\end{itemize}

\cvproject{Kernel space RTP data encryption, decryption, padding, and ptime modification [2013]}
\begin{itemize}
    \item A step to speed up the heavy weight encryption-decryption of RTP data.
    %by doing this in kernel space. 
    While user space time modification slows up, kernel space modification can speed up the process.
\end{itemize}



%% -------------------------------------------------
%%      SKILLS
%% -------------------------------------------------
\cvsection{Skills}
\vspace{-5pt}
% \begin{table}[]
    \begin{tabular}{ll}
        \textbf{\begin{tabular}[c]{@{}l@{}}Language\\ {}\end{tabular}}  &   \begin{tabular}[c]{@{}l@{}}C, C++, Java, Swift 2.1, Javascript,\\ Python, R, \TeX \end{tabular}                \\
        \textbf{Framework}                                              &   Spring Boot, Django                                                                               \\
        \textbf{\begin{tabular}[c]{@{}l@{}}Paradigm\\ {}\end{tabular}}  & \begin{tabular}[c]{@{}l@{}}Reactive Programming (RX), \\ REST API, OpenMP, MPI, CUDA\end{tabular} \\
        \textbf{Database}                                               &   MySql, Mongo                                                                                      \\
        \textbf{Version Controller}                                     &   Git, Bitbucket, Gitlab                                                                            \\
        \textbf{Management}                                             &   JIRA, Trello, Redmine                                                                             \\
        \textbf{\begin{tabular}[c]{@{}l@{}}Others\\ {}\end{tabular}}    &   \begin{tabular}[c]{@{}l@{}}TDD, Firebase, Agile, Playbook, \\Code Review, Cont. Integration\end{tabular}           
    \end{tabular}
% \end{table}

% \cvskill{Language}{C, C++, Java, CUDA, Swift, Javascript, Python}
% \cvskill{Framework}{Spring Boot, Django}
% \cvskill{Paradigm}{Reactive Programming (RX), REST API, OpenMP, MPI, Cuda}
% \cvskill{Database}{MySql, Mongo}
% \cvskill{Version Controller}{Git}
% \cvskill{Management}{JIRA, Trello, Redmine}
% \cvskill{Others}{TDD, Firebase, Agile, Playbook}

%% -------------------------------------------------
%%      AWARDS
%% -------------------------------------------------
% \cvsection{Awards}
% \vspace{-5pt}
% \begin{itemize}
%     \item \textbf{Inter University Development Contest, 2013} - Second runner up for the development contest in \textit{php} track.
%     \item \textbf{Thesis Pre-defence Poster Presentation, 2013} - {$7^{th}$ in thesis pre-defence poster presentation among 60 teams.}
%     \item \textbf{Undergraduate National Scholarship, 2008-2014} - For outstanding performance in Higher Secondary exam.
%     \item \textbf{Secondary School National Scholarship, 2006-2008} - For excellent performance in Secondary School exam.
% \end{itemize}

%% -------------------------------------------------
%%      References
%% -------------------------------------------------
% \cvsection{References}
% \vspace{-5pt}
% Available upon request.




